%----------------------------------------------------------------------------------------
% James Casebeer — Resume
%----------------------------------------------------------------------------------------

\documentclass[11pt, letterpaper]{article}

% ---------- packages ----------
\usepackage[margin=0.75in, top=0.65in, bottom=0.65in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

\usepackage{fontspec}
\usepackage{xcolor}

% ---------- colours ----------
\definecolor{accent}{HTML}{2E4057}

% ---------- hyperlink style ----------
\hypersetup{
    colorlinks=true,
    urlcolor=accent,
    linkcolor=accent
}

% ---------- section formatting ----------
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0em}{}
  [\color{accent}\titlerule]

\titlespacing{\section}{0pt}{10pt}{4pt}

% ---------- list settings ----------
\setlist[itemize]{leftmargin=1.5em, itemsep=1pt, topsep=2pt, parsep=0pt}

%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%   HEADER
%----------------------------------------------------------------------------------------
\begin{center}
  {\LARGE\bfseries James Casebeer}\\[4pt]
  Richmond, VA \quad\textbar\quad Remote Available \quad\textbar\quad Open to relocation for the right opportunity\\[3pt]
  (703) 638-2390 \quad\textbar\quad
  \href{mailto:james.casebeer@gmail.com}{james.casebeer@gmail.com} \quad\textbar\quad
  \href{https://www.linkedin.com/in/james-casebeer-b64b4813b/}{LinkedIn} \quad\textbar\quad
  \href{https://github.com/jcasebeer}{GitHub}
\end{center}

%----------------------------------------------------------------------------------------
%   PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\section{Professional Summary}

C/C++ systems developer with 8 years of professional experience building and maintaining high-throughput, mission-critical software for enterprise document delivery platforms. Led a small development team and drove technical direction for on-premises software deployed across large enterprise ERP environments. Independently designed and built a 3D game engine from scratch in C++, featuring a physically based rendering pipeline, shadow mapping, an entity-component system, custom memory allocators, and multithreaded procedural mesh generation. Equally comfortable at the systems and graphics layers --- seeking a role where low-level performance and code quality matter.

%----------------------------------------------------------------------------------------
%   PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Professional Experience}

\noindent\textbf{Lead Product Developer} \hfill \textit{2021 -- Present}\\
\textit{STR Software --- Richmond, VA}\\[4pt]
\begin{itemize}
  \item Led development and long-term technical direction of core C/C++ software for an on-premises enterprise document delivery platform, deployed at customer sites processing \textbf{10,000+ documents per day}.
  \item Managed and mentored junior developers, conducting code reviews and providing technical guidance across the team.
  \item Drove architectural decisions to improve integration stability and throughput across ERP environments including Oracle and SAP.
  \item Sole developer on a port of the Linux build from 32-bit to 64-bit, requiring significant rework of platform assumptions baked into the original design while maintaining compatibility across Solaris, AIX, and HPUX.
  \item Owned feature development end-to-end, from design through deployment, for mission-critical print, fax, and email delivery systems.
\end{itemize}

\vspace{6pt}

\noindent\textbf{Junior Software Developer} \hfill \textit{2017 -- 2021}\\
\textit{STR Software --- Richmond, VA}\\[4pt]
\begin{itemize}
  \item Developed and maintained C/C++ components for ERP-to-hardware integration, focusing on high-throughput data handling and device communication across print, fax, and email delivery systems.
  \item Worked extensively with Unix system APIs including fork, select, and FIFO-based IPC for inter-process communication across the document delivery pipeline.
  \item Contributed to performance tuning, debugging, and feature work on a production codebase serving enterprise customers.
\end{itemize}

%----------------------------------------------------------------------------------------
%   SELECTED PROJECTS
%----------------------------------------------------------------------------------------
\section{Selected Projects}

\noindent\textbf{Gunswinger --- 3D Game Engine \& Game} \hfill \textit{Personal Project --- C++}\\
\textit{\textasciitilde20,000 lines \quad\textbar\quad Private repository, available on request}\\[4pt]
\begin{itemize}
  \item Designed and built a complete 3D game engine and game from scratch in C++.
  \item Implemented a physically based rendering (PBR) pipeline in OpenGL with custom GLSL shaders, including shadow mapping, normal mapping, and material workflows.
  \item Built an entity-component system (ECS) for decoupled, composable scene management.
  \item Wrote custom memory allocators to minimize heap fragmentation and improve cache performance in hot paths.
  \item Implemented multithreaded procedural mesh generation with optimizations targeting high-refresh-rate displays (120Hz+).
  \item Integrated GLFW for window/input management and miniaudio for audio playback.
\end{itemize}

\vspace{6pt}

\noindent\textbf{CGOL --- Cellular Automata Simulator} \hfill \textit{Personal Project --- C}\\
\href{https://github.com/jcasebeer/cgol}{\small\texttt{github.com/jcasebeer/cgol}}\\[4pt]
\begin{itemize}
  \item Built a terminal-based Conway's Game of Life simulator supporting arbitrary rulesets in Golly notation.
  \item Implemented a fixed 2D grid, real-time simulation, and a flexible command-line interface for custom cellular automata rules.
\end{itemize}

\vspace{6pt}

\noindent\textbf{Low-Level C Utilities} \hfill \textit{Personal Projects --- C}\\
\href{https://github.com/jcasebeer}{\small\texttt{github.com/jcasebeer}}\\[4pt]
\begin{itemize}
  \item \textbf{packer} --- Packs separate PBR textures (albedo, roughness, metallic) into combined textures, reducing memory usage and binding overhead in rendering systems.
  \item \textbf{radix\_sort} --- LSD radix sort implementation.
  \item \textbf{hash} --- Collection of custom hash table implementations.
  \item \textbf{marray} --- Dynamic array macros for efficient memory management in C.
\end{itemize}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\noindent\textbf{Bachelor of Science in Computer Science}\\
George Mason University \hfill \textit{Graduated 2017}

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}

\noindent
\begin{tabular}{@{} l l}
  \textbf{Languages}         & C, C++ (C++17/20), Java, Python \\[3pt]
  \textbf{Graphics \& Audio} & OpenGL, GLSL, GLFW, miniaudio, ImGui \\[3pt]
  \textbf{Rendering}         & Physically Based Rendering, Shadow Mapping, Texture/Channel Packing \\[3pt]
  \textbf{Systems}           & Multithreading, Custom Memory Allocators, Performance Optimization, \\
                             & Data Structures \& Algorithms, Unix IPC (fork, select, FIFO) \\[3pt]
  \textbf{Platforms}         & Linux (RHEL, Alpine), Solaris, AIX, HPUX \\[3pt]
  \textbf{Tools}             & CMake, GCC/Clang, GDB, Make, Visual Studio, Git, SQLite, stb\_image \\[3pt]
  \textbf{Other}             & ECS Architecture, Procedural Generation, ERP Integration (Oracle, SAP) \\
\end{tabular}

\end{document}
